LogChunks: A Data Set for Build Log Analysis

### 2020-01-15 msr-paper/paper.tex
Done until l480

In our opinion, the width and depth of the \emph{LogChunks} data set
make it an ideal benchmark for automated build log analysis
techniques.
\end{abstract}

@@

\todo{mention most popular repositories very briefly somewhere?}
\todo{80x -> 80}
\begin{figure}[tbp]
	\centering
	\includegraphics[width=\columnwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{overview.pdf}
	\caption{Overview of \emph{LogChunks}}
	\label{fig:lc-overview}
\end{figure}

\section{Creating LogChunks}
This section presents how we gathered the logs for \emph{LogChunks} and our manual labeling process.
\label{sec:data-collection}

@@

To sample the builds for \emph{LogChunks} we let \texttt{TravisRequester} check up to 1000 builds per repository and keep ten of the status \emph{failed}~\cite{travis2009buildstatus}.
%A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.

\paragraph{Log Sampling}
Travis CI build comprise of a number of jobs that actualize a build
process in a defined environment. As such, the outcome from different
jobs might be different. For each build in LogChunks, we download the
first job which has the same state as the overall build.

We inspected the collected build logs and discarded logs from three repositories.
One had only one failed build, two others had empty build logs on Travis CI\@.
In total we collected 797 logs from 80 repositories spanning 29 languages.

\subsection{Labeling Process}
\label{sec:labeling-process}
After collecting a wide range of Travis CI build logs we manually labeled which text chunk describes why the build failed.
Following that, we assigned search keywords and structural categories to each log chunk.

@@

\section{Data Set Validation}
\label{sec:validation}
% We validate our collected data points in two different ways.
% A different labeler performed a second pass of labeling the build failure reason, keywords and structural categories on a subset of the data.
% In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set.
% We asked them whether our retrieval of the log part describing the reason the build failed was correct.
%This sections describes these two validation studies.
Following we present the two studies we conduct to validate the labeled data in \emph{LogChunks}.

\subsection{Inter-Rater Reliability Study}
To evaluate the validity of our labeled data we perform a second labeling of a sample of the data in \emph{LogChunks}.

\paragraph{Method}
We followed the same labeling process as described in Section~\ref{sec:labeling-process}.
For the build failure reason and the keywords, we presented 30 randomly sampled build logs from distinct repositories in \emph{LogChunks}.
The structural categories are relative to other logs from the same repository.
Therefore, we randomly sampled 3 repositories and presented all 10 examples within them to the second labeler.

\paragraph{Results}
For the substring describing why the build failed, the two labelers exactly agreed in six cases.
In 15 cases the second labeler selected more lines, in five their selections overlapped and in four they completely disagreed.
Regarding the keywords, the two labelers completely agreed in nine cases and completely disagreed in two cases.
In nineteen cases there was overlap in the keywords of the two labelers.%, in two the first labeler selected additional keywords compared to the second, while the second labeler proposed additional keywords in seven cases.
When classifying the chunks into structural categories, the two labelers agreed in 26 cases and disagreed in four cases.

@@

% For the structural categories this validation study showed a high overlap.
% In our instructions to the second labeler we did not emphasize the \emph{structural} aspect enough.
% They sorted into categories along \emph{why} the build failed, putting failing tests from different test runners into the same category even though the failing tests were presented differently in the log.
%
Our main learning from this study is that it is important and difficult to adequately communicate all decisions and assumptions on how data is labeled.
We reviewed the misunderstandings and incorporated more thorough descriptions in Section~\ref{sec:data-schema}.

\subsection{Developer Survey}
%For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
%As we are not involved in the development of any of the projects within our data set we could only rely on our previous experience with various build logs and systems.
%We only took the logs into account and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
%
%The person who probably knows best why a build failed is the one committing the changes which triggered the build.
%If the build was e.g.\ part of a pull request then developer likely inspected the failed build and tried to fix the build so the pull request can be accepted.
We sent out mails to the original developers whose commits triggered the builds represented in \emph{LogChunks} and asked them whether the log chunk we labeled actually describes why the build failed.
This section describes our survey and discusses our results.

\paragraph{Method}
Using the Travis API, we collect the commit information for each build represented in \emph{LogChunks}.
We grouped all commits triggered by one developer and sent out an mail to them.%, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
%Figure~\ref{fig:dev-mail} shows one of the mails sent out.
The mail included links to the corresponding commits, build overview and log file.
We asked the developers to fill out a short survey in case our extraction was not correct.
%Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
In the survey, we asked the developer to paste in the log part actually describing the failure reason or describe in their own words why we were wrong.
As some of the chunks we labeled are many lines long, we trimmed all down to 10 lines to keep the mail readable.

\paragraph{Results}
In total we sent out mails to 246 developers.%, asking about 3.2 build logs per mail on average.
32 of these mails could not be delivered, e.g.\ because they were addressed to \emph{noreply} addresses.
%These 32 mails related to 68 of the build logs.
We received answers from 61 developers, corresponding with 144 build logs.
%Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds} show the proportions of mails and logs answered about, not delivered and unanswered.

Of the 144 answers, 132 said our extraction was correct.
%26 answered either ``close, but not quite correct'' or ``no, the build failed for another reason''.
We manually inspected the 26 negative answers and found that some stated that the proposed extraction did not show the whole description of why the build failed.
This is because we had to trim long chunks to keep the mails readable.
After adjusting these answers, 12 answers stated that our labeled log chunk was not correct.

\paragraph{Discussion}
This study highly strengthens the trust in the validity of the labeled log chunks.
The study received answers about 18\% of the logs from \emph{LogChunks}.
After manual correction, 91\% of the received answers said our labeled chunks were accurate.

One of our extractions only showed a warning and the developer proposed to also include the line stating that warnings are treated as errors.
In others that were identified as incorrect, we labeled the error message of an error that was later ignored.

@@

\subsection{Automatic data.}
%We give a description of the manually labeled data.
%\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
%Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
LogChunks comprises information on \todo{x} build logs, which are organized in folders for each language and repository.
Within a repository folder, there are folders for each of the general build status ('successful', 'failed', ...), which contain the entire unaltered log files.
% the logs are separated according to build status.
%Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
%The build status folder contains the full logs in files named with the ID of the build that produced the log.
For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
Figure \ref{tab:data-in-example} presents the data within each example.

\lstset{
  language=XML,
  morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
	frame=single,
	escapeinside=**
}
\begin{figure}[]
	\centering
\begin{lstlisting}[breaklines=true]
<Examples>
  <Example>
    <Log>C/php@php-src/failed/529279089.log</Log>
      <Keywords>ERROR, FAIL, DIFF</Keywords>
      <Category>0</Category>
      <Chunk>001+ ** ERROR: process timed out **
001- OK.
========DONE========
FAIL Bug #60120 (proc_open hangs)</Chunk>
  </Example>
  ...
</Examples>
\end{lstlisting}
	\caption{Example XML file from \emph{LogChunks}}
	\label{lst:examples}
\end{figure}

\begin{figure*}[htbp]
\centering
\begin{tabularx}{\textwidth}{@{}lXlX@{}}
  \toprule
  & Description & Unit & Example \\
  \midrule
  Log & relative path to the input build log & Path to Log File & Haskell/koalaman@shellcheck/failed/501296412.log \\
  Chunk & log chunk that describes why the build failed & String & shellcheck.hs:442:19: error:
    Variable not in scope: doesPathExist :: [Char] -> IO Bool \\ 
  Keywords & keywords the authors would use to search for the log chunk & Strings & Failures, FAILURE, FAILED \\ 
  Category & categorization of the structural representation of the log chunk within the build log & Integer & 0 \\
  \bottomrule
\end{tabularx}
\caption{Data within an example in \emph{LogChunks}}
\label{tab:data-in-example}
\end{figure*}

>>>>

The width and depth of the \emph{LogChunks} data set are intended to
make it the default benchmark for automated build log analysis
techniques.
\end{abstract}

@@

\todo{mention most popular repositories very briefly somewhere?}
\todo{Match subsection titles with descriptions in picture}
\todo{80x -> 80}
\begin{figure}[tbp]
	\centering
	\includegraphics[width=\columnwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{overview.pdf}
	\caption{Overview of \emph{LogChunks}}
	\label{fig:lc-overview}
\end{figure}

\section{Creating LogChunks}
This section presents how we gathered the logs and our manual labeling process.
\label{sec:data-collection}

@@

To sample the builds for \emph{LogChunks} we check up to 1,000 builds per repository and keep ten of the status \emph{failed}~\cite{travis2009buildstatus}.
%A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.

\paragraph{Log Sampling}
Travis CI builds comprise a number of jobs that actualize a build
process in different environments. Hence, the outcome from different
jobs might be different. For each build in LogChunks, we download the
first job which has the same state as the overall build.

\todo{what does it mean to only have one failed build? wouldn't you
  exclude the entire repository then?}  We inspected the collected
build logs and discarded logs from three repositories.  One had only
one failed build, two others had empty build logs on Travis CI\@.  In
total, we collected 797 logs from 80 repositories spanning 29
languages.

\subsection{Labeling Process}
\label{sec:labeling-process}
After collecting build logs, the first author manually labeled which
text chunk describes why the build failed.  Following that, she
assigned search keywords and structural categories to each log chunk.

@@

\subsection{Validation}
\label{sec:validation}
\todo{how is the validation embedded in the data set? is there a special flag for validated entries?}
\todo{how many entries are validated?}

We validate our collected data points via an initial inter-rater
reliability study, and a cross-validation with developers.

\subsection{Inter-Rater Reliability Study}
\todo{I am thinking to cut this ... it does not give much, results are a bit underwhelming (why not calculate kappa?), and the meat lies in the developer study anyway}

\paragraph{Method}
The second author of this paper performed the same labeling process as described in \Cref{sec:labeling-process}, on 30 randomly sampled build logs from distinct repostories.
He extracted the build failure reason and the keywords.
The structural categories are relative to other logs from the same repository.
Therefore, we randomly sampled 3 repositories and presented all 10 examples within them to the second labeler.

\paragraph{Results}
\todo{Can we shorten this?}
For the substring describing why the build failed, the two labelers exactly agreed in six cases.
In 15 cases the second labeler selected more lines, in five their selections overlapped and in four they completely disagreed.
Regarding the keywords, the two labelers completely agreed in nine cases and completely disagreed in two cases.
In nineteen cases was there overlap in the keywords of the two labelers.
When classifying the chunks into structural categories, the two labelers agreed in 26 cases and disagreed in four cases.

@@

% For the structural categories this validation study showed a high overlap.
% In our instructions to the second labeler we did not emphasize the \emph{structural} aspect enough.
% They sorted into categories along \emph{why} the build failed, putting failing tests from different test runners into the same category even though the failing tests were presented differently in the log.
%
Our main learning from this study is that it is important and difficult to adequately communicate all decisions and assumptions on how data is labeled.
We reviewed the misunderstandings and incorporated more thorough descriptions in \cref{sec:data-schema} to guide the design for our external validation.

\subsection{Developer Validation}
%For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
%As we are not involved in the development of any of the projects within our data set we could only rely on our previous experience with various build logs and systems.
%We only took the logs into account and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
%
%The person who probably knows best why a build failed is the one committing the changes which triggered the build.
%If the build was e.g.\ part of a pull request then developer likely inspected the failed build and tried to fix the build so the pull request can be accepted.

In our second validation, we sent out emails to the original
developers whose commits triggered the builds represented in
\emph{LogChunks} and asked them whether the log chunk we labeled
actually describes why the build failed.  This section describes our
survey and discusses our results.

\paragraph{Method}
Using the Travis API, we collected the commit information for each build represented in \emph{LogChunks}.
We grouped all commits triggered by one developer and sent out an email to them.%, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
%Figure~\ref{fig:dev-mail} shows one of the mails sent out.
It included links to the corresponding commits, build overviewm and log file.
We asked the developers to fill out a short form in case our extraction was not correct.
%Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
In the survey, we asked the developer to paste in the log part actually describing the failure reason or describe in their own words why our original extraction was incorrect.

\paragraph{Results}
In total we sent out mails to 246 developers. 32 of these mails could
not be delivered. We received answers from 61 developers, corresponding to
144 build logs (response rate: 24.8\%).

Of the 144 answers, 132 indicated our extraction was correct.
%26 answered either ``close, but not quite correct'' or ``no, the build failed for another reason''.
We manually inspected the 26 negative answers and found that some stated that the proposed extraction did not show the whole description of why the build failed.
This is because we had to trim long chunks to keep the mails readable.

After adjusting for these answers, 12 answers remained that stated that our labeled log chunk was not correct.

\paragraph{Discussion}
We believe that our developer survey highly strengthens the trust in
the validity of the labeled log chunks.  The study received answers
for about 18\% of the data in \emph{LogChunks}.  After manual
correction, 91\% of the received answers said our labeled chunks were
accurate.  One possible threat regarding the high number of correct
answers is that, since we show the error message we extracted, it
might be operationally easier for developers to validate it, rather
than search for it in a long log file. To alleviate this problem, we
made it as easy to confirm as to reject an extracted log chunk. We
only ask for more details (the correct log chunk) in a second step.

One of our 12 incorrect extractions only showed a warning and the
developer proposed to also include the line stating that warnings are
treated as errors. In others, we labeled the error message of an error
that was later ignored.

%We give a description of the manually labeled data.
%\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
%Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
LogChunks comprises information on \todo{x} build logs, which are organized in folders for each language and repository.
Within a repository folder, there are folders for each of the general build status ('successful', 'failed', ...), which contain the entire unaltered log files.
% the logs are separated according to build status.
%Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
%The build status folder contains the full logs in files named with the ID of the build that produced the log.
For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
\Cref{tab:data-in-example} presents the data LogChunks contaians for an examplatory build from koalaman@shellcheck each example.

\lstset{
  language=XML,
  morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
	frame=single,
	escapeinside=**
}
\begin{figure}[]
	\centering
\begin{lstlisting}[breaklines=true]
<Examples>
  <Example>
    <Log>C/php@php-src/failed/529279089.log</Log>
      <Keywords>ERROR, FAIL, DIFF</Keywords>
      <Category>0</Category>
      <Chunk>001+ ** ERROR: process timed out **
001- OK.
========DONE========
FAIL Bug #60120 (proc_open hangs)</Chunk>
  </Example>
  ...
</Examples>
\end{lstlisting}
	\caption{Example XML file from \emph{LogChunks} \todo{Isn't this exactly the same as Figure 2? Only keep one?}}
	\label{lst:examples}
\end{figure}

\begin{figure*}[htbp]
\centering
\begin{tabularx}{\textwidth}{@{}lXlX@{}}
  \toprule
  Data & Description & Unit & Example \\
  \midrule
  Log & Relative path to the input build log & Path & \tt{Haskell/koalaman@shellcheck\newline/failed/501296412.log} \\
  Chunk & Log chunk that describes why the build failed & String & \tt{shellcheck.hs:442:19: error:
    Variable not in scope: doesPathExist :: [Char] -> IO Bool} \todo{is this strictly one?} \\ 
  Keywords & Keywords the authors would use to search \todo{only search or also actually FIND it?} for the log chunk & List of Strings & \tt{Failures, FAILURE, FAILED} \\ 
  Category & Categorization of the structural representation of the log chunk within the build log \todo{can you explain what this means?} & Integer & \tt{0}\\
  \todo{what about validation info?}\\
  \bottomrule
\end{tabularx}
\caption{Examplary, complete data excerpt from \emph{LogChunks} for a failed build in \tt{koalaman@shellcheck}.}
\label{tab:data-in-example}
\end{figure*}

@@
